Simulations

### 2020-12-09 Simulations.Rmd
Update Simulations.Rmd

# The Model
```{r, set.seed(0)}
# There are three key parameters: the probability that the worst team in the league beats the best team in a random game (given by 'p'), the standard deviation in game-to-game performance levels for each team (given by 'tao'), and the standard deviation in the team talent levels (given by 'sigma'). We as the researchers choose a value for p or the ratio of tao and sigma.
p = 0.25
tao = 4.28
sigma = 1

@@

  top6 <- rbind(central[1:3,],pacific[1:3,])
  top6 = top6[order(-top$totalPoints),]

>>>>

# The Model
```{r, set.seed(400)}
# There are three key parameters: the probability that the worst team in the league beats the best team in a random game (given by 'p'), the standard deviation in game-to-game performance levels for each team (given by 'tao'), and the standard deviation in the team talent levels (given by 'sigma'). We as the researchers choose a value for p or the ratio of tao and sigma.
p = 0.25
tao = 4.28
sigma = 1

@@

  top6 <- rbind(central[1:3,],pacific[1:3,])
  top6 = top6[order(-top6$totalPoints),]
